### 2022-02-23 sections/introduction.tex
updates with EB comments

%This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
The analysis reported here targets Higgs boson decays to 
%This paper is focused on the decay mode of the Higgs boson into
$\tau$-leptons with the complete Run~2 dataset collected in 2015-2018. The corresponding integrated luminosity is 139 fb$^{-1}$. Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted. The dataset is divided into several final states depending on the production mode and
the  $W$ decay. Top pair production events where the W boson decays hadronically (leptonicall) are referred to as $t_h$ ($t_l$). The contribution of 
$W\rightarrow\tau\nu$ is included as $\tau_{\text{lep}}$ in $t_l$ when the $\tau$ decays into a light lepton (electron or muon) or as $\thad$ 
in $t_h$ when the $\tau$ decays hadronically.
%either hadronically or leptonically from the $t\rightarrow Wb$ decay, which are referred as $t_h$ and $t_l$. The contribution of $W\rightarrow\tau\nu$ is included either in
%$t_l$ when the $\tau$ decays into a light lepton (electron or muon) as $\tau_{\text{lep}}$ or in $t_h$ when the $\tau$ decays hadronically as $\thad$.
The $H\rightarrow \tau\tau$ decay is detected in
either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_l$). 
Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are named hadronic channels. Events with at least one \tauhad with an additional electron or muon are named leptonic channels. More signal regions are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data~\cite{fcnc36}.
In addition, an improved treatment of misidentified $\tau$-leptons in simulation and data-driven
fake estimations from multi-jet background are implemented.
% and more
%$$t\bar{t}$ control regions (CRtt) are used for calibration of misidentified (fake) taus in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
Finally, a multivariate technique based on boosted decision trees, is used to discriminate between the signal and the background on the basis of their different kinematics distributions.

>>>>

%This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
The analysis reported here targets Higgs boson decays to 
%This paper is focused on the decay mode of the Higgs boson into
$\tau$-leptons with the complete Run~2 dataset collected in 2015-2018. The corresponding integrated luminosity is 139 fb$^{-1}$. Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted. The dataset is divided into several final states depending on the production mode and
the  $W$ decay. Top pair production events where the W boson decays hadronically (leptonicall) are referred to as $t_h$ ($t_{\ell}$). The contribution of 
$W\rightarrow\tau\nu$ is included as $\lep$ in $t_{\ell}$ when the $\tau$ decays into a light lepton (electron or muon) or as $\thad$ 
in $t_h$ when the $\tau$ decays hadronically.
%either hadronically or leptonically from the $t\rightarrow Wb$ decay, which are referred as $t_h$ and $t_l$. The contribution of $W\rightarrow\tau\nu$ is included either in
%$t_l$ when the $\tau$ decays into a light lepton (electron or muon) as $\tau_{\text{lep}}$ or in $t_h$ when the $\tau$ decays hadronically as $\thad$.
The $H\rightarrow \tau\tau$ decay is detected in
either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_{\ell}$). 
Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are named hadronic channels. Events with at least one \tauhad with an additional electron or muon are named leptonic channels. More signal regions are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data~\cite{fcnc36}.
In addition, an improved treatment of misidentified $\tau$-leptons in simulation and data-driven
fake estimations from multi-jet background are implemented.
% and more
%$$t\bar{t}$ control regions (CRtt) are used for calibration of misidentified (fake) taus in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
Finally, a multivariate technique based on boosted decision trees, is used to discriminate between the signal and the background on the basis of their different kinematics distributions.
